RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-07-04 discussion.tex

\subsection{Open issues}
\label{sect:goalmodeling:openissues}

@@

>>>>

\todo{Marc}{all}{Review the following notes:

\begin{itemize}
\item RE17 paper: merging argumentation theory with law
  "Using Argumentation to Explain Ambiguity in Requirements Elicitation Interviews" Yehia Elrakaiby, Alessio Ferrari, Paola Spoletini, Stefania Gnesi and Bashar Nuseibeh
\item more details on Murukannaiah [RE15]
\item related work on argumentation theory
\item First paper we wrote they also said something about Bashar Nuseibeh
\item Also mention argumentation in AI and how that relates to our work
\item Also paper by Daniel Amyot that he once sent to us:
  "Synergy between Activity Theory and goal/scenario modeling for requirements elicitation, analysis, and evolution"
\item Maybe this one:
  "Complete Traceability for Requirements in Satisfaction Arguments"
  Anitha Murugesan, Michael Whalen, Elaheh Ghassabani and Mats Heimdahl
  (University of Minnesota, United States)

\item  At least we can say our work is different from this if it is unrelated..
\item We should make the comparison more in depth.
\item Look at related work of Jureta and see how it is related with us.
\item Maybe the papers above (e.g., Bashar) have related work that relates to us as well.
\end{itemize}
}
\subsection{Open issues}
\label{sect:goalmodeling:openissues}

@@

\todo{Marc}{all}{Finish this}

### 2017-07-04 examples.tex

The transcript excerpt of this example is shown in Table~\ref{table:transcript:decomposition} in the appendix and comes from transcript $t_3$. It consists of a discussion about the type of decomposition relationship for the goal \texttt{Simulate}.

>>>>

\todo{Marc}{all}{Check whether the text matches the figure here}
The transcript excerpt of this example is shown in Table~\ref{table:transcript:decomposition} in the appendix and comes from transcript $t_3$. It consists of a discussion about the type of decomposition relationship for the goal \texttt{Simulate}.
